How to Name a Real-World Object, and how not to

### 2019-12-07 papers/ACL2020/related.tex

\paragraph{(Entry-Level) Object Names}

@@

\paragraph{Visual Object Recognition in Computer Vision}
- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image)\\
- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?

>>>>

\paragraph{(Entry-Level) Object Naming}

@@

\paragraph{Visual Object Recognition in Computer Vision}
- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image). It predicts the class of the most salient object in an image. \\
- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?
